Novelty Detection Using Graphical Models for Semantic Room Classification

### 2011-05-17 semantic-nd/article.tex
Removed authors and institutions for blind review.
Changes on explaning the order of the input space for novelty thresholding.

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{André Susano Pinto}
%
%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Faculdade de Engenharia da Universidade do Porto, Portugal\\
\url{andresusanopinto@gmail.com}\\
\url{http://url}}

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}
\maketitle

@@

% Explain threshold approach to novelty detection
Due to the desire of robustness, a novelty detection system would
always possess some threshold that describes on how strict the system should be to
new samples. This threshold describes a trade between error and rejection: as the
more the system tries to reduce rejection the more prone to produce
errors it becomes.
This threshold if often seen as a max allowed distance between a sample and the known
class.

@@

Therefore any novelty system that decides to acknowledge a sample
$a$ as novel should also detect novelty on any sample $b$ satisfying
$P(\overline{novel}|b) < P(\overline{novel}|a)$.
As that would always reduce the error probability.
This way a novelty detection system is interested in defining an
order on all the possible inputs equivalent to the order defined by
the error rate: $P(\overline{novel}|x)$.

>>>>

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
\author{Removed for Blind Review}
%\author{André Susano Pinto, Andrzej Pronobis, Luis Paulo Reis}
%
%\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Removed for Blind Review}
%\institute{Faculdade de Engenharia da Universidade do Porto, Portugal\\
%\url{andresusanopinto@gmail.com}\\
%\url{http://url}}

\maketitle

@@

Adding capabilities to an agent to detect a normal sample allows to increase its
reliability. As a novelty signal can then be interpreted by the system to proceed
with more caution as its on the presence of a situation where its knowledge
does not correctly describes reality.

% Explain threshold approach to novelty detection
Due to the desire of robustness, a novelty detection system is often given the option
to reject normal samples. This is implemented as a threshold that describes a trade
between error and rejection: the more the system tries to reduce rejection, the more
prone to produce errors it becomes.

@@

Therefore any novelty system that decides to acknowledge a sample
$a$ as novel should also detect novelty on any sample $b$ satisfying
$P(\overline{novel}|b) < P(\overline{novel}|a)$.
As that would always reduce the error probability.
This way a novelty detection system is interested in defining an
order relation on all the possible inputs equivalent to the order defined by
the error rate: $P(\overline{novel}|x)$.
